---
title: "Chapter 1 HW"
author: "Ahmad M. Osman"
date: "9/7/2017"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE}
#Set the working directory
setwd ("directory")
```

## Problem 1.19

```{r p1.19, echo=TRUE}
#Supply the file name for problem 1.19
gpa <- read.table("CH01PR19.txt",header=F,col.names=c("GPA","ACT"))
# This command makes data frame column names available as variables
attach(gpa)

# Plot the data
plot(ACT,GPA)

# Fit the regression model
fit <- lm (GPA ~ ACT)
fit
b1 <- fit$coeff[2]
b0 <- fit$coeff[1]
anova(fit)
ACTat30 <- b0 + b1*30
ACTat30
abline (b0,b1)
ACTat31 <- b0 + b1*31
ACTat31
ACTat31 - ACTat30
```
The intercept is 2.11 GPA units and the slope is 0.0388 GPA unit per ACT score increment.

Explanation: 
    
    a-	Β0 = 2.11405      Β1= 0.03883
    
        Y = 2.11405 + 0.03883 * X 
    
    b-	Yes. It looks good. 
    
    c-	GPA = 3.278863 for ACT = 30.
    
    d-	The change = 0.03882713.
    

## Problem 1.20

```{r p1.20, echo=TRUE}
#Supply the file name for problem 1.20
machines <- read.table("CH01PR20.txt",header=F,col.names=c("minutes","copiers"))


# This command makes data frame column names available as variables
attach(machines)

# Plot the data
plot(copiers,minutes)

# Fit the regression model
fit <- lm (minutes ~ copiers)
fit
b1 <- fit$coeff[2]
b0 <- fit$coeff[1]
abline (b0,b1)
anova(fit)
```

Explanation: 
    
    a-	Y=-0.5802 + 15.0352 *X
    
    b-	The line fits well.
    
    c-	For 0 copiers, it takes -0.58 minutes.
    
    d- The mean service time for 5 copiers = 74.59608 minutes.
    
## Problem 1.21

```{r p1.21, echo=TRUE}
#Supply the file name for problem 1.21
aircraft <- read.table("CH01PR21.txt",header=F,col.names=c("broken ampules","shipment route"))

# This command makes data frame column names available as variables
attach(aircraft)

# Plot the data
plot(shipment.route,broken.ampules)

# Fit the regression model
fit <- lm (broken.ampules ~ shipment.route)
fit
b1 <- fit$coeff[2]
b0 <- fit$coeff[1]
abline(b0,b1)
points(mean(shipment.route),mean(broken.ampules), col='red')
```

Explanation: 
    
    a-	Y = 10.2 + 4.0 * X. Fits well. 

    b-	14.2

    c-	As the slope is 4, once we plug it into the equation, every time x increases by 1, makes the answer 4.  

    d-	Explained through the graph.
    
## Problem 1.22

```{r p1.22, echo=TRUE}
#Supply the file name for problem 1.22
Plastic <- read.table("CH01PR22.txt",header=F,col.names=c("Hardness","Time"))


# This command makes data frame column names available as variables
attach(Plastic)

# Plot the data
plot(Time,Hardness)

# Fit the regression model
fit <- lm (Hardness ~ Time)
fit
b1 <- fit$coeff[2]
b0 <- fit$coeff[1]
abline(b0,b1)
```

Explanation: 
    
    a-	Y = 2.034x + 168.600 

    b-	249.975

    c-	The point of estimate when hardness increases by one is equal the slope (2.034)
    
## Problem 1.23
    a- Using the formula "sum(fit$residuals)", the residual sum = -2.942091e-15. The residual is close to zero. The residual squared is 45.81761.
    b- The anova table stated that the MSE = 0.3883. Standard deviation is the results of the square root of the MSE = 0.623GPA.
    
## Problem 1.24
    a- Using the formula "sum(fit$residuals)", the residual sum = -1.176836e-14. The residual is close to zero. The residual squared is 3416.377.
    b- The anova table stated that the MSE = 79. Standard deviation is the results of the square root of the MSE, SQRT(79) = 8.888 minutes.

## Problem 1.25
    a- I residual for the first case is 1.8.
    b- MSE= 2.2. The variance is estimated by the MSE.